`ggmatplot`: An R package for data visualization on wide-format data

### 2022-02-28 Paper/paper.Rmd
middle initials for FH, corrected ANU affiliation

---
title: '`ggmatplot`: An R package for data visualization on wide-format data'
tags:
- R
- grammar of graphics
- ggplot2
- data visualisation
authors:
  - name: Xuan Liang
    orcid: 0000-0002-0792-3751
    affiliation: 1
  - name: Francis Hui
    orcid: 0000-0003-0765-3533
    affiliation: 1
  - name: Dilinie Seimon
    orcid: 0000-0003-4431-6077
    affiliation: 2
  - name: Emi Tanaka
    orcid: 0000-0002-1455-259X
    affiliation: 2
affiliations:
  - name: Australian National University
    index: 1
  - name: Monash University
    index: 2
citation_author: Liang et. al.
date: "`r Sys.Date()`"
year: 2022
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

>>>>

---
title: '`ggmatplot`: An R package for data visualization on wide-format data'
tags:
- R
- grammar of graphics
- ggplot2
- data visualisation
authors:
  - name: Xuan Liang
    orcid: 0000-0002-0792-3751
    affiliation: 1
  - name: Francis K. C. Hui
    orcid: 0000-0003-0765-3533
    affiliation: 1
  - name: Dilinie Seimon
    orcid: 0000-0003-4431-6077
    affiliation: 2
  - name: Emi Tanaka
    orcid: 0000-0002-1455-259X
    affiliation: 2
affiliations:
  - name: The Australian National University
    index: 1
  - name: Monash University
    index: 2
citation_author: Liang et. al.
date: "`r Sys.Date()`"
year: 2022
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---
